Double Trouble: Understanding Sex Differences in Synthetic Lethal interactions in Human Cancers \\~\\ Project Updates

### 2023-07-10 july18meeting_pres2/may30ccgmeeting.tex
updares

	\begin{frame}{Overall Project Workflow}
		content...
	\end{frame}

	\begin{frame}{Selection of TCGA Cancer Types}
		content...
	\end{frame}

>>>>

	\begin{frame}{Overall Project Workflow}
		\includegraphics[width=12cm, height=5.2cm]{img2.png}
	\end{frame}

	\begin{frame}{Selection of TCGA Cancer Types}
			\begin{columns}
				\begin{column}{0.45\textwidth}
					\includegraphics[width=5cm, height=8cm]{img1.png}
				\end{column}
				\begin{column}{0.5\textwidth}
					\begin{itemize}
						\item There is a lack of healthy tissue RNA-seq samples in the TCGA database (12 cancers with more than 10 pairs in M and F)
					\end{itemize}
				\end{column}
			\end{columns}

		\includegraphics[width=5cm, height=8cm]{img1.png}
	\end{frame}

	\begin{frame}{Creating Pan-Cancer Expression Matrices}
		content...
	\end{frame}

	\begin{frame}{Normalizing Pan-Cancer Expression Matrices}
		content...
	\end{frame}
